MONID

### 2023-09-11 Presentation/presentation.tex
update

>>>>

    \begin{block}{Interpretation note.}    
        The difference between maximal and minimal becomes important only when we are evaluating the at the boundaries of a trace; $\underline{\text{max}}$ rules evaluates at $\underline{\text{true}}$ at initial and final istants, while $\underline{\text{min}}$ rules evaluates at $\underline{\text{false}}$.
    \end{block}
